A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-04-28 icml_2018_monolitic_end_to_end/doc/main.tex
Updates the paper

\title{WEVE: Weighted Enhancement Using Variance Estimation}

@@

\begin{abstract}
This paper presents a new robust neural frontend layer referred to as Power
Normalized Neural Frontend (PNNF) for robust speech recognition. PNNF
is implemented as a layer in an end-to-end all neural-network speech 
recognition system. For speech recognition, features such as Mel Filterbank
Cepstral Coefficient (MFCC) or log-Mel have been used very widely.
More recently, features motivated by human auditory processing have shown
improvement under certain conditions. Nevertheless, these auditory
features are constructed using signal processing blocks with hand-crafted
parameters for certain conditions. Therefore, the performance is not
always optimal for various kind of acoustic conditions.
 PNNF frontend layer is loosely motivated by human auditory system.
This processing uses the concept of the auditory masking and the auditory nonlinearity.
However, instead of directly using theories and parameters about human auditory masking,
neural networks make decision about it from the training data.
Even though the structure of the PNNF layer is very simple, this layer
significantly boosts the performance of the speech recognition system.
\end{abstract}

@@

\section{Feature enhancement}

In the feature enhancement process, we estimate a clean feature 
$\vec{y}$ given a corrupt feature $\vec{x}$.

In this case, the following $L_2$ norm is widely used:
\begin{align}
  l(\vec{y}, \vec{x}) = 
\end{align}

Feature mapping is a process of mapping noisy feature vectors
to clean feature vectors to enhance robustness
\cite{C_Kim_ASRU_2009_1, k_han_taslp_2015_00, k_han_icassp_2014_00}.
This procedure may be formulated by the following equation:
\begin{align}
  Y() = X()
\end{align}

From noisy features, we may infer 
Another

Masking and feature mapping are closely related techniques.
In feature mapping, enhanced features are predicted from
noisy features using machine learning models
The masking-based approaches with
Joint Adaptive Training (JAT) have been shown
to be effective to a large training set
\cite{a_narayanan_interspeech_2015_1}.

\section{Structure of the neural front-end}

\subsection{Neural nonlinearity}
In this section, we describe our neural nonlinearity algorithm. 
\begin{align}
  \vec{q[m, l]} = \vec{x[m, l]} ^ {\vec{\alpha}} 
\end{align}

\subsection{Neural background removal}
In this section, we describe our Neural Background Removal (NBR) approach.
Fig. \label{fig:nbr_diagram} shows the structure of the NBR processing.

$\vec{q}$ is the non-linearity output defined in

\begin{figure}
    \centering
    \resizebox{80mm}{!}{%
         \input{../figures/background_removal.tex}} %
    \caption {
      The structure of the Neural Background Removal (NBR) block.
      \label{fig:nbr_diagam}
    }
    %\end{center}
\end{figure}

\subsection{  }

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2017/}
\end{center}

Please read carefully the instructions below and follow them
faithfully.

\section{The structure of the SPL algorithm}

@@

%\begin{figure}
%    \centering
%    \resizebox{80mm}{!}{%
%         \input{../figures/entire_diagram.tex}} %
%    \caption {
%      The structure of feature enhancement using peak
%      value normalization and LSTMs.
%      \label{fig:entire_diagam}
%    }
%    %\end{center}
%\end{figure}

Fig. \ref{fig:entire_diagram} shows the structure for enhancing
noisy feature.

\subsection{Simulated utterance generation}
We use the room simulation system introduced in
\cite{C_Kim_INTERSPEECH_2017_1} to generate noisy speech
from clean speech.
\begin{align}
  y[n]
\end{align}
For 
\subsection{Review of the Room Simulator for Data Augmentation}
%
%
%\begin{figure}
%  \centering
%    \begin{subfigure}{\linewidth}
%      \centering
%      \includegraphics[width=70mm]{room_diagram.eps}
%      \caption{}
%      \label{fig:room_diagram}
%    \end{subfigure}
%   \\
%    \begin{subfigure}{\linewidth}
%      \centering
%      \includegraphics[width=70mm]{image_method.eps}
%      \caption{}
%      \label{fig:image_method}
%    \end{subfigure}
%    \caption{
%    (a) A simulated room: There may be multiple microphones, a single target
%    sound source, multiple noise sources in a cuboid-shape room with
%    acoustically reflective walls. (b) A diagram showing the location
%    of the real and the virtual sound sources assuming that the walls
%    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
%  \vspace{-10mm}
%\end{figure}
%
%
In this section, we briefly review the structure of the Google
Room Simulator for generating simulated utterances
to train acoustic models for speech recognition systems
\cite{C_Kim_INTERSPEECH_2017_1}. We assume a room of a
rectangular cuboid-shape as shown in Fig. \ref{fig:room_diagram}.
Assuming that all the walls of a room reflect acoustically uniformly,
we use the image method to model the Room Impulse Responses (RIRs)
\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007, S_G_McGovern_RIR}.

Fig. \ref{fig:image_method} shows how virtual sources
appearing as empty circles are constructed in the image method.
Even though the virtual rooms appear to be created in two-dimensions
in Fig. \ref{fig:image_method}, in the ``\emph{Room Simulator}",
they are constructed in three-dimensions. For example, in our
work for training the acoustic model for Google Home, we consider
$17 \times 17 \times 17 = 4913$ virtual rooms for RIR calculation
\cite{C_Kim_INTERSPEECH_2017_1}.
Following the image method, the impulse response is calculated
using the following equation
\cite{ J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007}:
\begin{align}
    h[n] = \sum_{i = 0}^{I-1} \frac{r^{g_i}}{d_i}
    \delta \left[n -\left \lceil{\frac{d_i f_s}{c_0}}\right \rceil \right],
      \label{eq:h_n_calculation}
\end{align}
where $i$ is the index of each virtual sound source, and $d_i$ is the distance
from that sound source to the microphone, $r$ is
the reflection coefficient of the wall, $g_i$ is
the number of the reflections
to that sound source, $f_s$ is the sampling rate of the RIR, and $c_0$ is the
speed of sound in the air. We use the value of $f_s = 16,000$ \textit{Hz} and
$c_0 = 343$ \textit{m/s} for the room simulator \cite{B_Li_INTERSPEECH_2017_1}.
For $d_i$, $r$, we use numbers created by a random number generator
following specified distributions for each impulse response \cite{C_Kim_INTERSPEECH_2017_1}.

Assuming that there are $I$ sound sources including one target
source and $J$ microphones, the received signal at microphone
$j$ is given by:
\begin{align}
  y_j[n] =  \sum_{i=0}^{I-1} \alpha_{ij} \left(h_{ij}[n] * x_i[n]\right).
  \label{eq:y_j_def}
\end{align}
Since we used a two-microphones system in
\cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1},
$J$ is two, and for the number noise sources, we used a value from zero
up to three \cite{C_Kim_INTERSPEECH_2017_1}.
%

@@

\subsection{Feature normalization using the peak-value}

The power-mel coefficients $q_x[m, l]$ and $q_y[m, l]$
are obtained from the clean and the simulated noisy
speech $x[n]$ and $y[n]$ respectively. $q_{x, \text{peak}}$
and $q_{y, \text{peak}}$

\section{Estimation of the expected value and the variance
  of the enhanced feature from the noisy feature}
\label{sec:estimation}

\begin{figure}
    \centering
    \resizebox{80mm}{!}{%
         \input{../figures/training.tex}} %
    \caption {
      Training of neural networks to estimate the clean feature and error ratio from corrupt feature
      \label{MFCCPNCCComparison}
    }
    %\end{center}
\end{figure}

>>>>

\title{A state of the art end-to-end speech recognition algorithm with
a homogenous structure.}

@@

\begin{abstract}
TODO(chanw.com) Revise the abstract.
This paper proposes a new end-to-end speech recognition system referred to
as Recurrent neural network Sequence Classification (RSC). Recently, end-to-end speech
recognition systems have been gaining more attention from researchers and
several different structures have been proposed. Typical examples  
include Connectionist Temporal Classification (CTC), Recurrent Neural Network
  Transducer (RNN-T), and Sequence-to-Sequence Modeling using the attention
mechanism. The CTC-based approaches are using the CTC loss assuming the
conditional independence property. Although the structure of CTC is simpler
than other end-to-end systems, the performance is worse due to this conditional
independence assumption. RNN-T and attention-based approaches have distinct
components such as the prediction network  and encoder in RNN-T, and
the encoder, the decoder, and the attention layer in the attention-based model.
Compared to these models, SHC has a homogeneous structure from the bottom to 
the top layer. LSTM and max-pooling layer are repeated followed by the top
softmax layer. The embedded softmax output is fed back as input of each RNN
layer. The training starts with flat initialization and alignment is made
after every epoch. The loss is the Cross Entropy (CE) loss using this 
alignment result. In our experimental results, SHC algorithm has shown 
better performance than more complicated attention-based end-to-end speech
recognition system. Another major advantage is training is significantly
faster.
\end{abstract}

@@

Recently, deep neural network has significantly improved the performance
of speech recognition systems \cite{}.

\section{Review of end-to-end speech recognition systems}

\begin{figure}
    \centering
    \resizebox{40mm}{!}{%
         \input{../figures/ctc.tex}} %
    \caption {
      The entire structure of the sequence homogeneously-structured classifier
      (SHC).
      \label{fig:ctc_diagram}
    }
    %\end{center}
\end{figure}
Recently, there have been growing interests in end-to-end speech
recognition systems.  [CITE] Fig. \ref{fig:ctc_diagram} shows the
entire structure of the Connectionist Temporal Classification (CTC) 
and the attention-based end-to-end speech recognition system.

\section{Sequence Homogeneously-Structured Classifier}
Figure \ref{} shows the entire structure of the SHC. Speech-recognition
task can be also considered as a

\subsection{The structure of the Sequence Homogeneously-Structured Classifier}

@@

\begin{figure}
    \centering
    \resizebox{50mm}{!}{%
         \input{../figures/shc_diagram.tex}} %
    \caption {
      The entire structure of the sequence homogeneously-structured classifier
      (SHC).
      \label{fig:shc_diagram}
    }
    %\end{center}
\end{figure}

Fig. \ref{fig:shc_diagram} shows the structure of the SHC algorithm. The
structure is very simple and somewhat similar to that of CTC shown in TODO

\subsection{Training of the Sequence Homogeneously-Structured Classifier}
In this section, we describe how to train SHC. The procedure is summarized
in the following table.

\section{Structure of the Recurrent Sequence Recognizer}
\subsection{Review of the Room Simulator for Data Augmentation}
%
%
\begin{figure}
  \centering
    \begin{subfigure}{\linewidth}
      \centering
      \includegraphics[width=70mm]{room_diagram.eps}
      \caption{}
      \label{fig:room_diagram}
    \end{subfigure}
   \\
    \begin{subfigure}{\linewidth}
      \centering
      \includegraphics[width=70mm]{image_method.eps}
      \caption{}
      \label{fig:image_method}
    \end{subfigure}
    \caption{
    (a) A simulated room: There may be multiple microphones, a single target
    sound source, multiple noise sources in a cuboid-shape room with
    acoustically reflective walls. (b) A diagram showing the location
    of the real and the virtual sound sources assuming that the walls
    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
  \vspace{-10mm}
\end{figure}
%
%
%
\subsection{Viterbi alignment and N-best alignment}

In conventional frame-wise CE-training, forced-alignment 
has been performed to obtain the frame-level acoustic unit  
boundaries. TODO(chanwcom) Even though the Viterbi algorithm
has advantages in simplicity and efficiency, it is based on
the conditional independence assumption.

@@
